Analyses

### 2020-06-15 analyses.Rmd
- implemented feedback from ST

```{r}
fig_fs_m <- ggplot(
  gather(d_fs, variable, value, -version) %>% 
    mutate(variable = factor(variable, levels = var_names_breaks)),
  aes(x = version, y = value, fill = version)) +
  stat_summary(fun.y = mean, geom = "bar") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .75) +
  facet_wrap(~ variable, nrow = 2) + 
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        plot.title = element_text(hjust = .5),
        panel.spacing = unit(.9, "lines"),
        text = element_text(size = 12),
        legend.position="bottom",
        legend.title = element_blank()) +
  coord_cartesian(ylim = c(0, 7)) +
  scale_fill_brewer(palette="Greys")
fig_fs_m
```

>>>>

```{r}
fig_fs_m <- ggplot(
  gather(d_fs, variable, value, -version) %>% 
    mutate(variable = factor(variable, levels = var_names_breaks)),
  aes(x = version, y = value, fill = version)) +
  stat_summary(fun.y = mean, geom = "bar") +
  stat_summary(aes(label=round(..y.., 2)), fun.y = mean, geom = "text", 
               vjust = 2, size = 3) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .75) +
  facet_wrap(~ variable, nrow = 2) + 
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        plot.title = element_text(hjust = .5),
        panel.spacing = unit(.9, "lines"),
        text = element_text(size = 12),
        legend.position="bottom",
        legend.title = element_blank()) +
  coord_cartesian(ylim = c(0, 7)) +
  scale_fill_brewer(palette="Greys")
fig_fs_m
```
